Errorless irrationality: removing error-driven components from the inverse base-rate effect paradigm

### 2023-01-10 docs/manuscript.tex
include future research

% Asymmetric representation can arise in different ways.
The hypothesised way asymmetric representation is manifested is the attentional tuning of cognitive representation of category exemplars.

- auxiliary phenomenon (Wills CIRP addition)
- Things that any theory of IBRE should explain
- current theories fall short
- eye-tracking and attention
- attention can still be allocated asymmetrically to drive the distinguishability of categories.

>>>>

% Asymmetric representation can arise in different ways.
One hypothesised way asymmetric representation is manifested is the attentional tuning of cognitive representation of category exemplars.
This is not necessarily absent in our experiment, but is not directly tested.
Our experiments do not give direct evidence against the role of attention in developing the asymmetric representation.
Nonetheless, it must not happen through an error-driven process as conceptualised in most prominent theories.
To further investigate this, the cued-recall IBRE procedure could incorporate eye-tracking to measure dwell time and order of information encoding.
Even if we observe more and longer fixations to C relative to B, attention can still be allocated asymmetrically to drive the distinguishability of categories.
Explanations do not need to invoke an explicit error-driven process.

- auxiliary phenomenon (Wills CIRP addition)
- Things that any theory of IBRE should explain
- current theories fall short
- eye-tracking and attention
-
